Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-04-17 automatica/paper.tex
added all benchmarks to Table 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Cruise Control  & 1 &   &  &  &  & & & &\\
2  & DC Motor          & 2 &   &  &  &  & & & &\\
3  & Helicopter        & 3 &  &   &  &  & & & &\\
4  & Inverted Pendulum & 4 &   &  &  & & & & &\\
5  & Magnetic Pointer  & 2 & &  &  &  & & & &\\
6  & Magnetic Suspension & 2 &  & & & & & & &\\
7  & Pendulum          & 2 &   & & & & & & &\\
8  & Suspension        & 2 &  & & & & & & &\\
9  & Tape Driver       & 3 &   & & & & & & &\\
10 & Satellite          & 2 &   &  & & & & & &\\\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}

>>>>

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Acrobot  & &   &  &  &  & & & &\\
2  & Antenna  & &   &  &  &  & & & &\\
3  & Ballmaglev  & &  &   &  &  & & & &\\
4  & Bioreact & &   &  &  & & & & &\\
5  & Chen\_ex1  & & &  &  &  & & & &\\
6  & Chen\_ex2 & &  & & & & & & &\\
7  & Chen\_ex3 & &   & & & & & & &\\
8  & Chen\_ex4 & &  & & & & & & &\\
9  & Cruise  & &  & & & & & & &\\
10 & CruiseHSCC  & &   &  & & & & & &\\
12 & Cstr & &   &  & & & & & &\\
13 & Cstr tmp  & &   &  & & & & & &\\
14 & DCmotor   & &   &  & & & & & &\\
15 & Flexbeam   & &   &  & & & & & &\\
16 & Guidance chen   & &   &  & & & & & &\\
17 & Helicopter   & &   &  & & & & & &\\
18 & Invpendulum\_cart   & &   &  & & & & & &\\
19 & Invpendulum\_pen   & &   &  & & & & & &\\
20 & Magpointer   & &   &  & & & & & &\\
21 & Magsuspension  & &   &  & & & & & &\\
22 & Pendulum   & &   &  & & & & & &\\
23 & Regulator   & &   &  & & & & & &\\
24 & Invpendulum\_pen   & &   &  & & & & & &\\
25 & Spring mass dump   & &   &  & & & & & &\\
26 & streamdrum   & &   &  & & & & & &\\
27 & Suspension  & &   &  & & & & & &\\
28 & Tapedriver   & &   &  & & & & & &\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}
